SDR enhancement by clouds

### 2024-03-12 article/article.Rmd
Commit 2024-03-12 11:11

```{r echo=FALSE, fig.cap="Trend of the yearly excess energy"}
knitr::include_graphics("../images/energy-1.png")
```

```{r echo=FALSE, fig.cap="Trend of the excess energy per CE"}
knitr::include_graphics("../images/energy-3.png")
```

@@

```{r echo=FALSE, fig.cap="Distribution of the number of CE cases per week"}
knitr::include_graphics("../images/climCE_week-1.png")
```

```{r echo=FALSE, fig.cap="Distribution of the number of CE cases per doy"}
knitr::include_graphics("../images/climCE_daily-1.png")
```

```{r echo=FALSE, fig.cap="Distribution of the number of CE cases per doy"}
knitr::include_graphics("../images/clim_CE_N_doy-1.png")
```

```{r echo=FALSE, fig.cap="Trend of the excess energy per CE"}
knitr::include_graphics("../images/energy-2.png")
```

### Yearly plots relative to all GHI data.

```{r echo=FALSE, fig.cap=""}
knitr::include_graphics("../images/rel_energy-1.png")
```

```{r echo=FALSE, fig.cap=""}
knitr::include_graphics("../images/rel_energy-2.png")
```

```{r echo=FALSE, fig.cap=""}
knitr::include_graphics("../images/rel_energy-3.png")
```

>>>>

```{r echo=FALSE, fig.cap="Treds of the mean over irradiance per CE"}
knitr::include_graphics("../images/energy-3.png")
```

```{r echo=FALSE, fig.cap="Trend of number of CE cases"}
knitr::include_graphics("../images/energy-2.png")
```

```{r echo=FALSE, fig.cap="Trend of the yearly excess energy due to CE over irradiance"}
knitr::include_graphics("../images/energy-1.png")
```

@@

<!-- ```{r echo=FALSE, fig.cap="Distribution of the number of CE cases per week"} -->
<!-- knitr::include_graphics("../images/climCE_week-1.png") -->
<!-- ``` -->

<!-- ```{r echo=FALSE, fig.cap="Distribution of the number of CE cases per doy"} -->
<!-- knitr::include_graphics("../images/climCE_daily-1.png") -->
<!-- ``` -->

<!-- ```{r echo=FALSE, fig.cap="Distribution of the number of CE cases per doy"} -->
<!-- knitr::include_graphics("../images/clim_CE_N_doy-1.png") -->
<!-- ``` -->

<!-- ### Yearly plots relative to all GHI data. -->

<!-- ```{r echo=FALSE, fig.cap=""} -->
<!-- knitr::include_graphics("../images/rel_energy-1.png") -->
<!-- ``` -->

<!-- ```{r echo=FALSE, fig.cap=""} -->
<!-- knitr::include_graphics("../images/rel_energy-2.png") -->
<!-- ``` -->

<!-- ```{r echo=FALSE, fig.cap=""} -->
<!-- knitr::include_graphics("../images/rel_energy-3.png") -->
<!-- ``` -->
